Dynein walks like an Imperial AT-ST

### 2018-09-12 papers/paper/paper-supplemental.tex
Break up model figs into a simpler one for the main paper and a more detailed one for the supplemental

\section*{Deriving motion equations}
\subsection*{Onebound case}
The following equations allow recursive calculation of the positions of each domain in Cartesian coordinates:

@@

>>>>

\section*{Deriving motion equations}

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.49\linewidth]{figures/onebound-cartoon.pdf}
\includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
\caption{}
\label{fig:supp-model}
\end{figure}

\subsection*{Onebound case}
The following equations allow recursive calculation of the positions of each domain in Cartesian coordinates:

@@

\section*{Fitting spring constants}
How we fit spring constants; maybe plot the 3d correlation-color scatter plot for 3 springs

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.7\linewidth]{../../plots/randomsearchplot.pdf}
\caption{\textbf{Fitting spring constants through homology to experimental stepping data.} \textit{A.} 3D scatter plot of simulations color-coded by the sum-of-squares error between the model and experimental stepping histograms. \textit{B-D:} Scatter plots of spring constants and error; orange dots indicate averages over nearest 25 points.}
\label{fig:supp-model}
\end{figure}

### 2018-09-12 papers/paper/paper.tex

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Describe our algorithm in sufficient detail.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\item Add force-dependent plots to compare with yildiz?
\end{enumerate}

\subsection{John}
\begin{enumerate}
\item Proofread the algorithm description, improve its writing, and
  check against code.
\item Figure out how to do no-unbinding simulations to get Yildiz
  comparison data.  Also this gives us unbinding rates that will agree
  with our stepping time, etc. \verb!src/simulate_unbinding_rates.cpp!
\item Play with parameters to get stepping length histogram more
  reasonable (this automatically gives us the velocity).
\item Run long/many simulations with final parameters.
\item Run a low-ATP simulation for comparison data.
\item Nice final version of stepping length histogram.
\item Nice final version of tension-gating Yildiz comparison.
\item Consider a no-binding simulation and a separable model.  Create
  a figure demonstrating/testing whether the histogram of final
  displacement is independent of initial displacement.
\item Consider a simple Monte Carlo that just uses our no-unbinding
  and no-binding simulations to model dynein (like Yildiz).
\end{enumerate}

>>>>

\subsection{Elliott}
\begin{enumerate}
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item When we have all data, write discussion
\item Rewrite introduction
\item Possibly sample stalk angles at high resolution and also 50ms, to show why the low time resolution in Lessinger prevented them from seeing the powerstroke?
\item Test suite for paper plots to see if there aren't subtle bugs?
\end{enumerate}

\subsection{John}
\begin{enumerate}
\item Proofread the algorithm description, improve its writing, and
  check against code.
\item Run a low-ATP simulation for comparison data.
\item Consider a no-binding simulation and a separable model.  Create
  a figure demonstrating/testing whether the histogram of final
  displacement is independent of initial displacement.
\item Consider a simple Monte Carlo that just uses our no-unbinding
  and no-binding simulations to model dynein (like Yildiz).
\end{enumerate}
